Analysis of nested multilevel Monte Carlo \\ using approximate Normal random variables

### 2021-02-16 paper.tex
Updated a few references.

\author{
Mike Giles
\thanks{\href{mailto:mike.giles@maths.ox.ac.uk}%
{\texttt{mike.giles@maths.ox.ac.uk}}}
\and 
Oliver Sheridan-Methven
\thanks{\href{mailto:oliver.sheridan-methven@maths.ox.ac.uk}%
{\texttt{oliver.sheridan-methven@maths.ox.ac.uk}}}
}

@@

The three approximations are all motivated by the different hardware features 
of modern CPUs and GPUs (manycore graphics processing units). The 
implementation details and the resulting execution performance of 
the three approximations are explained more fully in \cite{sheridan-methven20}.

Note that we are not concerned with the computational cost of generating the 
uniform random numbers $U$.  This is because we can follow 
Giles et al.~\cite{ghmr19b} in using a trick due to 
Bakhvalov \cite{bakhvalov64} to very efficiently 
generate a set of uniformly-distributed values $\{ U_1, U_2, \ldots\}$ 
with pairwise independence (i.e.~for any two indices $i\neq j$, $U_i$ 
is independent of $U_j$) at a cost of less than 3 computer operations, 
on average.
In essence, the procedure is very similar to the \emph{digital shift} 
used to transform Sobol' points in a randomised Quasi Monte Carlo 
computation \cite{ecuyer18}.

@@

\newpage

\bibliographystyle{unsrt}
\bibliography{../../../tex/bib/mlmc,../../../tex/bib/mc}

>>>>

\author{
Mike Giles
\thanks{\href{mailto:mike.giles@maths.ox.ac.uk}%
{\texttt{mike.giles@maths.ox.ac.uk}}}
\and 
Oliver Sheridan-Methven
\thanks{\href{mailto:oliver.sheridan-methven@hotmail.co.uk}%
{\texttt{oliver.sheridan-methven@hotmail.co.uk}}}
}

@@

The three approximations are all motivated by the different hardware features 
of modern CPUs and GPUs (manycore graphics processing units). The 
implementation details and the resulting execution performance of 
the three approximations are explained more fully in \cite{sheridanmethven2020approximating,sheridan-methven2020thesis}.

Note that we are not concerned with the computational cost of generating the 
uniform random numbers $U$.  This is because we can follow 
Giles et al.~\cite{ghmr19b} in using a trick due to 
Bakhvalov \cite{bakhvalov64} to very efficiently 
generate a set of uniformly-distributed values $\{ U_1, U_2, \ldots\}$ 
with pairwise independence (i.e.~for any two indices $i\neq j$, $U_i$ 
is independent of $U_j$) at a cost of less than 3 computer operations, 
on average.
In essence, the procedure is very similar to the \emph{digital shift} 
used to transform Sobol' points in a randomised Quasi Monte Carlo 
computation \cite{ecuyer2016randomized}.

@@

\bibliographystyle{unsrt}
\bibliography{mlmc,mc}
